---
title: "test"
output: pdf_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```


```{r data_load, echo = F, warning=F, message=F, error=FALSE}
########################################################################
### Load packages and data ---------------------------------------------

## Packages
library(tidyverse)
library(broom)
library(corrplot)
library(knitr)
library(stargazer)
library(scales)
library(rgdal)
library(rgeos)
library(grid)
library(gridExtra)

## Regression data files
agg_df <- read_csv(file = 'sfg-aqua-data/phils_regression_df_1980to2012.csv') # aggregate provincial data from 1980 to 2012 
species_df <- read_csv(file = 'sfg-aqua-data/phils_regression_df_species_2002to2014.csv') # species level provincial data from 2002 to 2012

## Map data files
# shapefile map data
provmap <-readOGR(dsn = '../../Google Drive/Project Data/phils-data/Provinces', layer = 'Provinces', stringsAsFactors = F)

# Order of municipalities and provinces in shapefile and corresponding polygon id number
prvs <- toupper(provmap@data$NAME_1)

# lookup table for matching provinces to polygon ids
lktable2 <- data_frame(prvs, 'id' = as.character(c(0:(length(prvs)-1)))) %>%
  rename(province_name  = prvs)
```

## Abstract
Traditionally, fishers and farmers have been treated as competitors (for space, within a market, for forage fish, for productivity), and fishers are often staunchly oppossed to aquaculture expansion. Aquaculture certainly interacts with wild fisheries in a number of ways, however the magnitude of these interactions is poorly known and quantified. This analysis uses provincial scale data on wild fisheries and aquaculture in the Philippines to examine if aquaculture activities impact wild fishery landings and value. Results show that, while aquaculture does indeed have a significant impact on wild fisheries, the impact is extremely small and varies by target fishery and aquaculture type (marine finfish, mussels, oysters, and seaweed). 

## Introduction

```{r intro_figures, echo=FALSE, message=F, warning=FALSE}
## Line plot
figs12_df <- agg_df %>%
  group_by(year) %>%
  summarize(`Wild fisheries`     = sum(all_catch, na.rm = T),
            `Aquaculture`        = sum(aqua_harvest_all, na.rm = T),
            `Municipal fisheries` = sum(muni_marine_catch, na.rm = T),
            `Commercial fisheries` = sum(comm_catch, na.rm = T)) %>%
  gather(key = 'Sector', value = 'Harvest', 2:5) %>%
  ungroup() %>%
  mutate(plot_num = 'A')

# Add panel assignments
figs12_df$plot_num[figs12_df$Sector %in% c('Municipal fisheries', 'Commercial fisheries')] <- 'B'

# add another aquaculture row for use in second panel
figs12_df <- figs12_df %>%
  filter(Sector == 'Aquaculture') %>%
  mutate(plot_num = 'B') %>%
  bind_rows(figs12_df)

fig1 <- figs12_df %>%
  ggplot(aes(x = year, y = Harvest, shape = Sector, linetype = Sector)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = comma) +
  scale_shape_manual(values = c('Aquaculture' = 0, 'Wild fisheries' = 1, 'Municipal fisheries' = 7, 'Commercial fisheries' = 10)) +
  labs(y = 'Production (metric tonnes, MT)',
       x = 'Year') +
  facet_wrap(~plot_num)


## Summary maps
# Map fishery catch by province
map1 <- left_join(lktable2, subset(agg_df, year == 2012)) # subset results to most recent year available
provmap <- tidy(provmap) # Tidy map to dataframe for mapping
provmap <- left_join(provmap, map1) # Join harvest data and map data

# Fish catch map
muni_catch_map <- ggplot(provmap, aes(x = long, y = lat, group = group, fill = muni_marine_catch)) +
  geom_polygon() +
  scale_fill_continuous(labels = comma)

# Aquaculture harvest map
muni_aqua_map <- ggplot(provmap, aes(x = long, y = lat, group = group, fill = aqua_harvest_all)) +
  geom_polygon() +
  scale_fill_continuous(labels = comma)

# Calculate % change in catch and aquaculture for all provinces and map with diverging scale
perc_change_df <- species_df %>%
  group_by(year, province_name) %>%
  summarize(catch = sum(fish_harvest, na.rm = T),
            aqua  = sum(aqua_harvest, na.rm = T)) %>%
  group_by(province_name) %>%
  mutate(catch_perc = 100*(catch[year == 2014] - catch[year == 2002]) / catch[year == 2002] ,
         aqua_perc = 100*(aqua[year == 2014] - aqua[year == 2002])/aqua[year == 2002]) %>%
  filter(year == 2014) %>%
  select(-year)

# Join percentages with map data
map2 <- left_join(lktable2, perc_change_df)

provmap2 <- left_join(provmap, map2) 

muni_perc_map_fish <- ggplot(provmap2, aes(x = long, y = lat, group = group, fill = catch_perc)) +
  geom_polygon() +
  scale_fill_gradient2(labels = comma, low = 'red', high = muted('green'))

# ggsave(filename = 'perc_change_catch.pdf')

muni_perc_map_aqua <- ggplot(provmap2, aes(x = long, y = lat, group = group, fill = aqua_perc)) +
  geom_polygon() +
  scale_fill_gradient2(labels = comma, low = 'red', high = muted('green'))

# ggsave(filename = 'perc_change_aqua.pdf')

# map_2 <- grid.arrange(muni_perc_map_fish, muni_perc_map_aqua, nrow = 1)
# 
# ggsave(filename = 'perc_change_map.pdf')

```

The Philippines is one of the world's major producers of seafood from both wild fisheries and aquaculture, ranking 12th and 5th respectively. Within national waters, fishery production steadily increased from `r figs12_df$Harvest[1]` metric tons (MT) in 1980 to `r figs12_df$Harvest[28]` MT in 2007, since which it has hovered around ~1.5 million MT. Fisheries management is decentralized in the Philippines, with national regulations granting municipalities jurisdiction over their nearshore municipal waters (< 15 km). As a result, fishery statistics in the Philippines are reported seperately for the municipal and commercial fleets, with the municipal fishery responsible for `r round(100*(figs12_df$Harvest[99] / figs12_df$Harvest[28]), digits = 1)` in 2012 (Figure 1).

```{r fig1, echo=FALSE, warning=F, message=F, fig.width=6, fig.height=2.5, fig.cap='Annual production (MT) by marine sector in the Philippines from 1980 to 2012'}
plot(fig1)
```

Although these regulations ban fishing by the commercial fleet in municipal waters, illegal encroachment is believed to be rampant, with scaled-down commercial vessels, referred to as *'baby trawlers'* operating extensively in municipal waters (Palomares, M. L. D., and D. Pauly, 2010). 

```{r, echo=F, warning=F, message=F, fig.width= 5, fig.height=5}

# Correlation matrix
# cor_df <- agg_df %>%
#   select(all_catch, muni_marine_catch, comm_catch, aqua_harvest_all, aqua_value, muni_value, comm_value, muni_price, comm_price, all_price) 
# 
# test <- cor(cor_df, use = 'complete.obs')
# 
# corrplot(test, addCoef.col = T)
```

## Materials and Methods
Data for this analysis comes from several sources. Fishery catch data for both the municipal and commercial sectors was obtained from the CountrySTAT Philippines data portal. These data include time series of catch (MT) and value for 31 species items organized by region and province.
