---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(scales)
library(forcats)
library(gridExtra)
library(readxl)

# Aquaculture data
aqua <- tbl_df(read.csv(file = '../../../Google Drive/Project Data/fao-data/FAO Aquaculture Data Final.csv', stringsAsFactors = F)) %>%
  # filter(Enviro %in% c('Marine', 'Brackishwater') & !grepl('Inland', AreaFAO)) %>%
  select(Country, CommName, SpeciesCatName, Enviro, AreaFAO, Year, AquaProduction, AquaValue, FoodCat) %>%
  rename(country      = Country,
         comm_name    = CommName,
         isscaap      = SpeciesCatName,
         enviro       = Enviro,
         fao_area     = AreaFAO,
         year         = Year,
         aqua_harvest = AquaProduction,
         aqua_value   = AquaValue)

aqua_ff <- aqua %>%
  filter(FoodCat == 'Food Fish')

# fishery data
fish <- tbl_df(read.csv(file = '../../../Google Drive/Project Data/fao-data/fao_capture_50to14.csv', na.strings = c('...','0 0','-'), stringsAsFactors = F)) %>%
  gather('Year',Catch,contains('X'),convert=T) %>%
  mutate(Year  = as.numeric(gsub('X','',Year)),
         Catch = as.numeric(gsub(pattern = ' F', replacement = '',Catch))) %>%
  filter(!`Country..Country.` %in% c('Totals - Quantity (tonnes)', 'Totals - Quantity (number)'))

# Commodities data
commods <- tbl_df(read.csv(file = '../../../Google Drive/Project Data/fao-data/Commodity_quantity_76to13.csv', na.strings = c('...','0 0', '-'), stringsAsFactors = FALSE)) %>%
                    gather('year','quantity',contains('X'),convert=T) %>%
                    mutate(year     = as.numeric(gsub('X','',year)),
                           quantity = as.numeric(quantity)) %>%
  rename(isscaap   = `Commodity..ISSCAAP.group.`,
         commodity = `Commodity..Commodity.` )
                  
commod_value <- read_csv(file = '../../../Google Drive/Project Data/fao-data/Commodity_value_76to13.csv')



# rename columns
colnames(fish) <- c('country', 'comm_name', 'sci_name', 'isscaap', 'fao_area', 'fao_code', 'units', 'year', 'catch')

exvessel <- read_excel(path = '../../price-db-sfg/price-db-data/FAO exvessel estimates from archives.xlsx', sheet = 1) %>%
  rename(isscaap = `Species group`,
         year    = Year, 
         exvessel   = Value) %>%
  select(isscaap, year, exvessel)

isscaap_touse <- c("Abalones, winkles, conchs",
                        "Clams, cockles, arkshells",
                        "Oysters",
                        "Mussels",
                        "Shrimps, prawns",
                        "Scallops, pectens",
                        "Miscellaneous marine molluscs",
                        "Miscellaneous coastal fishes",
                        "Salmons, trouts, smelts",
                        "Tunas, bonitos, billfishes",
                        "Miscellaneous pelagic fishes",
                        "Miscellaneous diadromous fishes",
                        "Marine fishes not identified",
                        "Cods, hakes, haddocks")
```

Define fed and unfed ISSCAAP categories

```{r}
unfed <- c("Brown seaweeds","Clams, cockles, arkshells","Green seaweeds",
           "Miscellaneous aquatic plants", "Miscellaneous marine molluscs",
           "Mussels","Oysters","Pearls, mother-of-pearl, shells","Red seaweeds")
```

```{r}
p3 <- aqua %>%
  filter(FoodCat == 'Food Fish' & year > 1975) %>%
  mutate(type = ifelse(enviro %in% c('Marine', 'Brackishwater'), 'Mariculture','Freshwater')) %>%
  group_by(type,isscaap,type,year) %>%
  summarize(production = sum(aqua_harvest, na.rm = T)) %>%
  filter(production > 0) %>%
  bind_rows(fish %>%
              filter(isscaap %in% .$isscaap & year >1975) %>%
              mutate(type = 'Fisheries') %>%
              group_by(type,isscaap,year) %>%
              summarize(production = sum(catch, na.rm = T))) %>%
  spread(type, production) %>%
  group_by(isscaap) %>%
  filter(all(is.na(Mariculture))==F) %>%
  gather(type, production, 3:5)
```

Make two panel plot of mariculture production
```{r}
p3 %>%
  filter(year %in% c(1980:2013)) %>%
  filter(type != 'Freshwater' & isscaap %in% isscaap_touse) %>% # comment out to remove freshwater 
  ungroup() %>%
  mutate(category = ifelse(isscaap %in% c("Abalones, winkles, conchs",
                        "Clams, cockles, arkshells",
                        "Oysters",
                        "Mussels",
                        "Scallops, pectens",
                        "Miscellaneous marine molluscs",
                        "Squids, cuttlefishes, octopuses"), 'Bivalves and molluscs', 'Marine finfish'),
         category = ifelse(isscaap %in% c("Shrimps, prawns"), 'Shrimps, prawns', category),
         category = ifelse(isscaap %in% c("Salmons, trouts, smelts", "Miscellaneous diadromous fishes"),
                           'Salmon and misc. diadromous fishes', category)) %>%
  group_by(category, type, year) %>%
  summarize(production = sum(production, na.rm = T)) %>%
  ggplot(aes(x = year, y = production/1e6, fill = type)) +
  geom_area() +
  scale_y_continuous(labels = comma) +
  scale_fill_brewer(palette = 'Set1') +
  facet_wrap(~category, nrow = 2) + 
  labs(y = 'Production (MMT)',
       x = 'Year',
       fill = 'Sector') +
  theme_bw() +
  theme(axis.title = element_text(size = 8),
        text = element_text(size = 8),
        legend.position = 'bottom',
        legend.title = element_text(size = 8))

# ggsave(filename = 'sfg-aqua-figures/figure_1_production.pdf', width = 5, height = 4.75)
```

```{r}
p3B <- p3 %>%
  filter(year %in% c(1994:2013)) %>%
  filter(type != 'freshwater') %>% # comment out to remove freshwater
  filter(isscaap %in% c("Miscellaneous coastal fishes",
                        "Salmons, trouts, smelts",
                        "Tunas, bonitos, billfishes",
                        "Miscellaneous pelagic fishes",
                        "Miscellaneous diadromous fishes",
                        "Miscellaneous demersal fishes",
                        "Marine fishes not identified",
                        "Cods, hakes, haddocks")) %>%
  ggplot(aes(x = year, y = production/1e6, fill = type)) +
  geom_area() +
  scale_y_continuous(labels = comma) +
  scale_fill_brewer(palette = 'Set1') +
  guides(fill = F) +
  facet_wrap(~isscaap, ncol = 4) +
  labs(y = 'Production (MMT)',
       x = 'Year',
       title = 'C') +
  theme_bw() +
  theme(legend.position = 'right',
        title = element_text(size = 14),
        axis.title = element_text(size = 8),
        legend.title = element_text(size = 8),
        text = element_text(size = 8))

# p3_final <- grid.arrange(p3A, p3B)

#ggsave(p3_final,filename = 'sfg-aqua-figures/sector_areas.pdf', width = 6, height = 8)
```

## Examine number of Commodities Per ISSCAAP group
```{r}
commods_per_isscaap <- commods %>%
  filter(is.na(quantity)==F & isscaap %in% isscaap_touse) %>%
  ungroup() %>%
  mutate(isscaap = fct_relevel(isscaap, isscaap_touse)) %>%
  group_by(isscaap, year) %>%
  summarize(number_commods = length(unique(commodity))) %>%
  ungroup()
  
ggplot(commods_per_isscaap, aes(x = year, y = number_commods, color = isscaap)) +
  geom_line() +
  guides(color = F) +
  facet_wrap(~isscaap, scales = 'free', nrow = 7, dir = 'v')
```



## Market Figure Methods
1. Use linkage tables from Melnychuk *et al.* (2016) to group aquaculture production by ISSCAAP group and calculate price for comparison with exvessel data.

```{r}
# Summarize aqua data by isscaap and year
aqua_pc <- aqua %>%
  filter(year > 1975) %>%
  filter(FoodCat == 'Food Fish' & year > 1975) %>%
  mutate(type = ifelse(enviro %in% c('Marine', 'Brackishwater'), 'Mariculture','Freshwater')) %>%
  group_by(isscaap, type, year) %>%
  summarize(aqua_harvest = sum(aqua_harvest, na.rm = T),
            aqua_value   = sum(aqua_value, na.rm = T),
            aqua_price   = 1000 * aqua_value / aqua_harvest) %>%
  left_join(commods_per_isscaap)
```

2. Join summarized aquaculture and exvessel data and filter out commodities with no aquaculture harvest

```{r}
comp <- exvessel %>%
  left_join(aqua_pc)
```

Run correlation test of mariculture and capture fisheries prices by ISSCAAP group
```{r}
price_cors <- comp %>%
  filter(isscaap %in% isscaap_touse & type == 'Mariculture') %>%
  group_by(isscaap) %>%
  summarize(price_cor = round(cor(exvessel, aqua_price),digits = 2),
            number_commods = mean(number_commods, na.rm = T))

price_cors %>%
  ggplot(aes(x = fct_reorder(isscaap, price_cor), y = price_cor, fill = price_cor)) +
  geom_label(aes(label = price_cor), size = 3) +
  scale_fill_gradient2(high = muted('green')) +
  geom_hline(yintercept = 0, linetype = 2, color = 'red') +
  guides(fill = F) +
  labs(y = 'Price Correlation Coefficient',
       x = 'ISSCAAP Species Group') +
  coord_flip() +
  theme_bw() +
  theme(axis.title = element_text(size = 10),
        text = element_text(size = 10))

# ggsave(filename = 'sfg-aqua-figures/price_correlations.pdf', width = 6, height = 4)
```


Plot average exvessel price against number of commodities and aquaculture species.
```{r}
comp %>%
  filter(isscaap %in% isscaap_touse & type == 'Mariculture') %>%
  group_by(isscaap) %>%
  mutate(scaled_exvessel = exvessel / exvessel[year == min(year, na.rm = T)]) %>%
  ggplot(aes(x = year, y = scaled_exvessel)) +
  geom_line() +
  # geom_point(aes(size = aqua_harvest), alpha = 0.6) +
  geom_hline(yintercept = 1, linetype = 2, color = 'red') +
  facet_wrap(~isscaap)
```


3. Plot average exvessel and ISSCAAP price over time by sector
```{r}
market_fig <- comp %>%
  # filter(isscaap %in% isscaap_touse) %>%
  filter(type == 'Mariculture') %>%
  filter(isscaap %in% c('Shrimps, prawns', 'Salmons, trouts, smelts')) %>%
  group_by(isscaap, year) %>%
  summarize(aqua = mean(aqua_price, na.rm = T),
            fish = mean(exvessel, na.rm = T)) %>%
  gather(metric, value, 3:4) %>%
  ungroup() %>%
  mutate(isscaap = fct_relevel(isscaap, isscaap_touse))


price_cors <- price_cors %>%
  filter(isscaap %in% c('Shrimps, prawns', 'Salmons, trouts, smelts')) %>%
  mutate(year = 2006,
         number_commods = round(number_commods)) %>%
         # isscaap = fct_relevel(isscaap, isscaap_touse)) %>%
  left_join(market_fig %>%
              group_by(isscaap) %>%
              summarize(axis_range = .15*max(value, na.rm = T)))


  ggplot(market_fig, aes(x = year)) +
  geom_label(data = price_cors, aes(x = 1998, y = axis_range , label = paste('Corr: ',price_cor,'\n', 'Commodities: ', number_commods), fill = price_cor), size = 2) +
  geom_line(aes(y = value, color = fct_rev(metric))) +
  scale_y_continuous(labels = comma, limits = c(0,NA)) +
  scale_fill_gradient2(high = 'lightgreen') +
  scale_color_brewer(palette = 'Set1') +
  guides(fill = F) +
  facet_wrap(~isscaap, scales = 'free_y', ncol = 3, dir = 'v') + 
  labs(x = 'Year',
       y = 'Price ($US/MT)',
       color = 'Sector') +
  theme_bw() +
  theme(axis.title = element_text(size = 10),
        legend.title = element_text(size = 10),
        text = element_text(size = 10),
        legend.position = 'bottom')
  
# ggsave(filename = 'sfg-aqua-figures/price_trends.pdf', width = 7, height = 8)  
```


```{r}
comp %>%
  filter(isscaap %in% isscaap_touse & type == 'Mariculture') %>%
  group_by(year) %>%
  summarize(aqua = mean(aqua_price, na.rm = T),
            Fisheries = mean(exvessel, na.rm = T)) %>%
  gather(metric, value, 2:3) %>%
  ungroup() %>%
  ggplot(aes(x = year, y = value, color = metric)) +
  geom_line() +
    labs(x = 'Year',
       y = 'Price ($US/MT)',
       color = 'Sector') +
  scale_y_continuous(labels = comma) +
  theme_bw() +
  theme(axis.title = element_text(size = 10),
        legend.title = element_text(size = 10),
        text = element_text(size = 10),
        legend.position = 'bottom')
  
```



4. Align production and price plots for same species

```{r, fig.height=8}
p4A <- p3A + facet_wrap(~isscaap, ncol = 1, scales = 'free_y')

p4B <- comp %>%
    # filter(year > 1993) %>%
    filter(isscaap %in% c("Abalones, winkles, conchs",
                        "Clams, cockles, arkshells",
                        "Oysters",
                        "Mussels",
                        "Shrimps, prawns",
                        "Scallops, pectens",
                        "Miscellaneous marine molluscs",
                        "Squids, cuttlefishes, octopuses")) %>%
  group_by(isscaap, year) %>%
  summarize(aqua = mean(aqua_price, na.rm = T),
            fish = mean(exvessel, na.rm = T)) %>%
  gather(metric, value, 3:4) %>%
  ggplot(aes(x = year, y = value, color = fct_rev(metric))) +
  geom_line() +
  scale_y_continuous(labels = comma, position = 'right') +
  scale_color_brewer(palette = 'Set1') +
  labs(y = 'Price ($US/MT)',
       fill = 'Sector',
       x = 'Year',
       title = 'B',
       color = 'Sector') +
  facet_wrap(~isscaap, scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = 'right',
        title = element_text(size = 14),
        axis.title = element_text(size = 8),
        legend.title = element_text(size = 8),
        text = element_text(size = 8))

p4 <- grid.arrange(p4A, p4B, ncol = 2, widths = c(2.75,3.25))

# ggsave(p4, filename = 'sfg-aqua-figures/production_price_plots4.png', height = 8, width = 6)

```

```{r, fig.height=8}
p5A <- p3B + facet_wrap(~isscaap, ncol = 1, scales = 'free_y')

p5B <- comp %>%
  # filter(year > 1993) %>%
  filter(isscaap %in% c("Miscellaneous coastal fishes",
                        "Salmons, trouts, smelts",
                        "Tunas, bonitos, billfishes",
                        "Miscellaneous pelagic fishes",
                        "Miscellaneous diadromous fishes",
                        "Miscellaneous demersal fishes",
                        "Marine fishes not identified",
                        "Cods, hakes, haddocks")) %>%
  group_by(isscaap, year) %>%
  summarize(aqua = mean(aqua_price, na.rm = T),
            fish = mean(exvessel, na.rm = T)) %>%
  gather(metric, value, 3:4) %>%
  ggplot(aes(x = year, y = value, color = fct_rev(metric))) +
  geom_line() +
  scale_y_continuous(labels = comma, position = 'right') +
  scale_color_brewer(palette = 'Set1') +
  labs(y = 'Price ($US/MT)',
       fill = 'Sector',
       x = 'Year',
       title = 'D',
       color = 'Sector') +
  facet_wrap(~isscaap, scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = 'right',
        title = element_text(size = 14),
        axis.title = element_text(size = 8),
        legend.title = element_text(size = 8),
        text = element_text(size = 8))

p5 <- grid.arrange(p5A, p5B, ncol = 2, widths = c(2.75,3.25))

ggsave(p5, filename = 'sfg-aqua-figures/production_price_plots5.png', height = 8, width = 6)

```

